Pass 3 Comparison

### 2024-05-21 studies/pass3_comparison.qmd
remove excluded studies from bib template

# sort by task
bib_df_merged <- bib_df_merged[order(bib_df_merged$PARADIGM),]
```

@@

```{r}
bib_df_merged$NOTES_INDEX.CA <- NULL
bib_df_merged$NOTES_INDEX.TE <- NULL
```

>>>>

# sort by task
bib_df_merged <- bib_df_merged[order(bib_df_merged$PARADIGM),]

# put rater notes side-by-side
NOTES.CA <- bib_df_merged$NOTES.CA
NOTES.TE <- bib_df_merged$NOTES.TE
bib_df_merged$NOTES.CA <- NULL
bib_df_merged$NOTES.TE <- NULL
bib_df_merged$NOTES_CA<-NOTES.CA
bib_df_merged$NOTES_TE<-NOTES.TE

@@

```{r}
bib_df_merged$NOTES_INDEX.CA <- NULL
bib_df_merged$NOTES_INDEX.TE <- NULL
bib_df_merged$CATEGORY <- NULL
```

## Get included studies

```{R}
bib_df_merged <- subset(bib_df_merged, final_decision == 'include')
bib_df_merged$final_decision <- NULL
```
